DP Problems of Interest

### 2012-10-19 docs/roadmap/problems.tex

\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm,hyperref,verbatim,pict2e,graphicx,marvosym,array,booktabs,nameref}
\hypersetup{
	%colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black
	urlbordercolor=1 0 0,linkbordercolor=0 1 1, citebordercolor=0 1 1,
}
\usepackage[usenames]{xcolor} % color names ,dvipsnames,svgnames,table
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\pagestyle{empty} % remove page numbers

\oddsidemargin 0.0cm
\evensidemargin 0.0cm
\topmargin 0.0cm
\headheight 0.0cm
\headsep 1.0cm
\textheight 21.0cm
\textwidth 16.0cm
\parskip 0.1cm
\parindent 0.0cm
\footskip 1.0cm

\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{8pt}{0pt}
\titlespacing{\subsection}{0pt}{8pt}{0pt}
\titlespacing{\subsubsection}{0pt}{8pt}{0pt}
\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\setenumerate{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
\def\ul{\begin{itemize}}
\def\ule{\end{itemize}}
\def\ol{\begin{enumerate}}
\def\ole{\end{enumerate}}

@@

\title{DP Problems of Interest}
\author{Manohar Jonnalagedda, Thierry Coppey, Nithin George}
\date{}
\begin{document}
\maketitle
\pagestyle{headings}

>>>>

\input{style.sty}

@@

\title{DP Problems of Interest}
\begin{document}
\maketitle
\pagestyle{headings}
